Trends of SDR in Thessaloniki

### 2023-06-07 Article.Rmd
Commit 2023-06-07 15:17

# documentclass:  article
# classoption:    a4paper,oneside
# fontsize:       12pt
# geometry:       "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
# link-citations: yes
# colorlinks:     yes
# urlcolor:       blue
# bibliography:   [references.bib]
# biblio-style:   apalike
# date:           "`r format(Sys.time(), '%F')`"
# 
# header-includes:
#   - \usepackage{caption}
#   - \usepackage{placeins}
#   - \captionsetup{font=small}
#   - \usepackage{setspace}\doublespacing
#   - \usepackage{float}

author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        bob@example.com
    affiliation:  Another University
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  1 main street
    city:         Thessaloniki
    state:        State
    postcode:     123456
    country:      Greece
  - code:         Another University
    organization: Department
    addressline:  A street 29
    postcode:     2054 NX
    city:         Manchester,
    country:      The Netherlands
footnote:
  - code:         1
    text:         "This is the first author footnote."
  - code:         2
    text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.

@@

output: 
  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
---

@@

## Long term trends

>>>>

# 
# header-includes:
#   - \usepackage{caption}
#   - \usepackage{placeins}
#   - \captionsetup{font=small}
#   - \usepackage{setspace}\doublespacing
#   - \usepackage{float}

author:
  - name:         Natsis Athanasios
    email:        natsisphysicist@gmail.com
    affiliation:  Laboratory of Atmospheric Physics
#    footnote:     1
    correspondingauthor: true
  - name:         Alkiviadis Bais
    email:        abais@auth.gr 
    affiliation:  Laboratory of Atmospheric Physics
    correspondingauthor: false
address:
  - code:         Laboratory of Atmospheric Physics
    organization: Aristotle University of Thessaloniki
    addressline:  Campus Box 149
    city:         Thessaloniki
    # state:        State
    postcode:     54124
    country:      Greece
#  - code:         Another University
#    organization: Department
#    addressline:  A street 29
#    postcode:     2054 NX
#    city:         Manchester,
#    country:      The Netherlands
# footnote:
#   - code:         1
#     text:         "This is the first author footnote."
#   - code:         2
#     text:         "Another author footnote."
abstract: |
  Study of GHI and DNI radiation for 'clear-sky' and all-sky conditions.

@@

output: 
  rticles::elsevier_article:
    keep_tex:         false
    citation_package: natbib
  bookdown::pdf_document2:
    number_sections:  no
    fig_caption:      yes
    keep_tex:         yes
    latex_engine:     xelatex
    toc:              yes
    toc_depth:        4
    fig_width:        7
    fig_height:       4.5
    documentclass:  article
    classoption:    a4paper,oneside
    fontsize:       12pt
# geometry:       "left=0.75in,right=0.75in,top=0.75in,bottom=0.75in"
# link-citations: yes
# colorlinks:     yes
# urlcolor:       blue
# bibliography:   [references.bib]
# biblio-style:   apalike
# date:           "`r format(Sys.time(), '%F')`"
---

@@

## Long-term trends
